### 2015-03-15 Docs/managing_jobs/managingjobs.tex
add a note about Edison problems with Cray 8.3.3 to 8.3.7 compilers...
fix typo
add some info on using yt in batch on titan

@@

\item Cray 8.3.0 generates an internal compiler error on edison/NERSC.
      To get back to the older Cray compilers, you need to do:
\begin{verbatim}                                                                   
module swap cce/8.3.0 cce/8.2.6
module swap cray-libsci cray-libsci/12.2.0
module swap cray-mpich cray-mpich/6.3.1
\end{verbatim}
\end{itemize}

>>>>

\subsection{Batch Submission of \yt\ Visualization Scripts}

You can run \yt\ python scripts in the titan batch queues
to do your visualization.  You need to install \yt\ and all its dependencies
manually somewhere on a LUSTRE filesystem---this ensures that the compute
nodes can see it.  A good choice is the project space, since that has
a longer purge window.

Once \yt\ is install by the {\tt install\_script.sh} script, it will tell
you what script to source to define the necessary paths.

The scripts {\tt process-titan.run} and {\tt parallel-yt-new} in
{\tt MAESTRO/Util/job\_scripts/titan/} will manage the yt jobs
by calling a python script for each file that matches a pattern.

@@

\item Cray 8.3.0 generates an internal compiler error on edison/NERSC.
      To get back to the older Cray compilers, you need to do:

\begin{verbatim}
module swap cce/8.3.0 cce/8.2.6
module swap cray-libsci cray-libsci/12.2.0
module swap cray-mpich cray-mpich/6.3.1
\end{verbatim}

\item Cray 8.3.3--8.3.7 compile, but issue a runtime error:
\begin{verbatim}
 BOXLIB ERROR: BOXARRAY_VERIFY_DIM: ba%dim not equal to some boxes dim:  3
\end{verbatim}
Again, the solution is to downgrade to the 8.2.6 version.
